---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# UtilsReportRSV

<!-- badges: start -->
<!-- badges: end -->

The goal of UtilsReportRSV is to provide utility
functions that facilitate easier, faster and more
reliable communication of data pre-processing and analysis.

## Installation

You can install the development version of UtilsReportRSV like so:

``` r
if (!requireNamespace("remotes", quietly = TRUE)) install.packages("remotes")
remotes::install_github("SATVILab/UtilsReportRSV")
```

## Uses

```{r example}
library(UtilsReportRSV)
```

### Display outputs by section with headings

```{r , include = FALSE}
set.seed(2106)
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")
library(ggplot2)
plot_list <- vapply(1:4, function(i) {
  p <- ggplot(
    data = data.frame(x = rnorm(20, mean = i))
  ) +
    geom_histogram(aes(x = x), bins = 20) +
    expand_limits(x = c(-3, 7))
  dir_save <- here::here("man/fig")
  if (!dir.exists(dir_save)) {
    dir.create(dir_save, recursive = TRUE)
  }
  fn <- file.path(dir_save, paste0("p_", i, ".png"))
  if (file.exists(fn)) return("")
  ggsave(
    filename = fn, plot = p, units = "cm",
    height = 7.5, width = 7.5
  )
  ""},
  ""
)
```

The function `loop_and display`  produces the following result, when using the `knitr` chunk option `results = "asis"`:
```{r , results = "asis"}
example_tbl <- data.frame(
  x = rep(c("Female", "Male"), each = 2),
  y = rep(c("Child", "Adult"), 2),
  path_plot = paste0(here::here(), "/man/fig/p_", 1:4, ".png"),
  stringsAsFactors = FALSE
)
loop_and_display(
  .tbl = example_tbl,
  .vars = c("x", "y"), 
  .f = function(df) {
    #print(df)
    cat(paste0("![](", df$path_plot, ")"), "\n")
    #knitr::include_graphics(df$path_plot)
  }
)
```

The function copy_file makes it easier to copy files by working out the final directory programmatically. Amongst other options,
one can ensure that the relative path from a particular directory is kept in the
final copied-to directory:
```{r }
dir_test <- file.path(tempdir(), "copy_file")
from <- file.path(dir_test, "folder1", "folder2", "folder3", "silly.txt")
if (!dir.exists(dirname(from))) dir.create(dirname(from), recursive = TRUE)
file.create(from)

copy_file(
  from = from,
  to_dir = file.path(dir_test, "testToDir"),
  keep_relative_path_from = file.path(dir_test, "folder1")
)
file.exists(
  file.path(dir_test, "testToDir", "folder2", "folder3", "silly.txt")
)
unlink(dir_test, recursive = TRUE)
```